### 2021-03-26 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/results.tex
added annotators comparison explain
computed comparison

Generally, a comparison of these heatmaps, indicate an increase in the recall rate of the methodology. This is due to the fact, that our proposed methodology is able to match a larger number of AAs, providing 50\% of the score to the syntactic match, thereby increasing the count of cells without a missing value. This approach is also able to reduce the impact of semantic matching from names, which might contain repeated words, such as ``patient" but in reality refer to disparate concepts, such as ``PatientName" and "PatientDateOfBirth". Another important aspect of our matching process is the inclusion of semantic concepts and suffixes, as a sentence before its conversion to an embedded vector. As discussed earlier, this process is used to reduce the impact of syntactic matches alone, which would give a higher score to the attributes ``PatientName" and ``PatientGender", which refer to different concepts. The inclusion of concepts behind ``Name" and ``Gender" part of these names, allow for an improved comparison. However, the evaluation of accuracy and precision rates necessitates the comparison of these methodologies with the ground truth. \textbf{annotation comparison}

>>>>

Generally, a comparison of these heatmaps, indicate an increase in the recall rate of the methodology. This is due to the fact, that our proposed methodology is able to match a larger number of AAs, providing 50\% of the score to the syntactic match, thereby increasing the count of cells without a missing value. This approach is also able to reduce the impact of semantic matching from names, which might contain repeated words, such as ``patient" but in reality refer to disparate concepts, such as ``PatientName" and "PatientDateOfBirth". Another important aspect of our matching process is the inclusion of semantic concepts and suffixes, as a sentence before its conversion to an embedded vector. As discussed earlier, this process is used to reduce the impact of syntactic matches alone, which would give a higher score to the attributes ``PatientName" and ``PatientGender", which refer to different concepts. The inclusion of concepts behind ``Name" and ``Gender" part of these names, allow for an improved comparison.

In order to evaluate the accuracy and precision rates of these methodologies, we then compared the results of our computed methods $D_f$, $D_b$, and $D_p$, with the average scored datasets by the human annotators. A visualization of the resultant Cohen's Kappa score for the 257 participating attributes, is shown in \textbf{figComputedComparisonKappaScore}. The bar chart shown in this visualization, indicates, an overall greater positive agreement between our proposed methodolody $D_p$, and the average scores of the annotators. The same is shown by the \textbf{orange} colored peaks in this dataset, which in all cases is either equivalent to the other approaches ($D_f$ and $D_b$), or better than them.
